Novel Sampling Using Stochastic Gradient Descent

### 2016-12-05 poster/main.tex
acknowledge

\small{\rmfamily{Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.}} \\

>>>>

\small{\rmfamily{We would like to thank Professor Martin Wainwright for his inspiring teaching this semster. And we also greatly appreciate Arturo Fernandez and Jeffery Chan, our GSIs, for their devotion in this course.}} \\
